---
title: "Hello R"
author: "William Harris"
date: "Data 2401"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

(Type your answer to Exercise 1 here. This exercise does not require any R code. **Remove notes like this in the final product that you turn in**)
``` There are a total of 1846 rows, 2 columns with variable names: "dataset" and "n".
```

```{r, echo = FALSE}
library(datasauRus)
library(dplyr)

datasaurus_dozen %>% 
  count(dataset) %>% 
  print(13)

```


### Exercise 2

(The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.)

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

(Add code and narrative as needed. Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient. To finish, remember to clean up the narrative by removing these instructions.)



```{r plot-star}


```

I'm some text, you should replace me with more meaningful text...
 
```{r cor-star}


```

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}


```

```{r}


```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
