---
title: "Hello R"
author: "William Harris"
date: "Data 2401"
output: 
  html_document: 
    highlight: espresso
    theme: yeti
    fig_width: 5
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1
## Retrieving data from the DatasauRus library:

``` There are a total of 1846 rows, 2 columns with variable names: "dataset" and "n".
```

```{r, echo = FALSE}
library(datasauRus)
library(dplyr)

datasaurus_dozen %>% 
  count(dataset) %>% 
  print(13)

```


### Exercise 2
## Plotting the Dino Dataset:
First let's plot the data in the dino dataset:

```{r plot-dino}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
  
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

## Plotting the Star dataset below:


```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

calculating the correlection between x,y in the star dataset: Both r values from the dino and star datasets have a negative- moderate linear relationship. 
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4

Both R values in dino and cirlce have a weak negative linear relationship

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x,y))

```

### Exercise 5

Plotting all of the datasets and summarizing correlation coeficients.
```{r plot-*, fig_width: 8}
library(datasauRus)
library(dplyr)

ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
 geom_point()+
 facet_wrap(~ dataset, ncol = 3) +
 theme(legend.position = "none")
 
datasaurus_dozen %>% 
 group_by(dataset) %>% 
 summarize(r = cor(x, y)) %>% 
 print(13)
```
