---
title: "Hello R"
author: "William Harris"
date: "Data 2401"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1
## Retrieving data from the DatasauRus library:

``` There are a total of 1846 rows, 2 columns with variable names: "dataset" and "n".
```

```{r, echo = FALSE}
library(datasauRus)
library(dplyr)

datasaurus_dozen %>% 
  count(dataset) %>% 
  print(13)

```


### Exercise 2
## Plotting the Dino Dataset:
First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
  
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

## Plotting the Star dataset below:


```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

calculating the correlection between x,y in the star dataset: Both r values from the dino and star datasets have a negative- moderate linear relationship. 
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x,y))

```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
